Milestone 2: Model Validation

### 2021-11-04 perf_release_criteria/milestone_3/ms_2_validation.Rmd

```

@@

```{r nn_mal_fs1, echo=FALSE}
nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1$matched, df_beta_val)
nn.mal.fs1.score <- score_model(bts, nn.mal.fs1$matched, df_rel_val)
nn.mal.fs1.score
```

Number of Beta samples: `r nrow(nn.mal.fs1$matched)`

```{r nn_mal_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs1$matched, df_beta_val, nn.mal.fs1.qq)
```

@@

```{r nn_mal_fs3, echo=FALSE}
nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
                        caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3$matched, df_beta_val)
nn.mal.fs3.score <- score_model(bts, nn.mal.fs3$matched, df_rel_val)
nn.mal.fs3.score
```
Number of Beta samples: `r nrow(nn.mal.fs3$matched)`

```{r nn_mal_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs3$matched, df_beta_val)
```

@@

```{r nn_mal_fs5, echo=FALSE}
nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
                        caliper = 0, calclosest = TRUE, ratio = 1, 
                        distance = "mahalanobis")
nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5$matched, df_beta_val)
nn.mal.fs5.score <- score_model(bts, nn.mal.fs5$matched, df_rel_val)
nn.mal.fs5.score
```

Number of Beta samples: `r nrow(nn.mal.fs5$matched)`

```{r nn_mal_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs5$matched, df_beta_val)
```

@@

```{r nn_logit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.logit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1$matched, df_rel_val)
nn.linear.logit.fs1.score
```

Number of Beta samples: `r nrow(nn.linear.logit.fs1$matched)`

```{r nn_logit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
```

@@

```{r nn_logit_fs3, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.logit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5$matched, df_rel_val)
nn.linear.logit.fs5.score
```

```{r nn_logit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
```

@@

```{r nn_gam_fs1, warning=FALSE, error=FALSE, echo=FALSE, message=FALSE}
nn.gam.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1$matched, df_beta_val)
nn.gam.fs1.score <- score_model(bts, nn.gam.fs1$matched, df_rel_val)
nn.gam.fs1.score
```

Number of Beta samples: `r nrow(nn.gam.fs1$matched)`

```{r nn_gam_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs1$matched, df_beta_val)
```

@@

```{r nn_gam_fs5, warning=FALSE, error=FALSE, echo=FALSE}
nn.gam.fs5 <- train_matchit(dfs[['4']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5$matched, df_beta_val)
nn.gam.fs5.score <- score_model(bts, nn.gam.fs5$matched, df_rel_val)
nn.gam.fs5.score
```

Number of Beta samples: `r nrow(nn.gam.fs1$matched)`

```{r nn_gam_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs5$matched, df_beta_val)
```

@@

```{r nn_probit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.probit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1$matched, df_rel_val)
nn.linear.probit.fs1.score
```

Number of Beta samples: `r nrow(nn.linear.probit.fs1$matched)`

```{r nn_probit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
```

@@

```{r nn_probit_fs5, warning=FALSE, error=FALSE, echo=FALSE}
nn.linear.probit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5$matched, df_rel_val)
nn.linear.probit.fs5.score
```

Number of Beta samples: `r nrow(nn.linear.probit.fs5$matched)`

```{r nn_probit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
```

@@

```{r genmatch_fs1, echo=FALSE}
genmatch.fs1.matched <- df_train_gen[fs1_results$matches$index.control,]
genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.matched, df_beta_val)
genmatch.fs1.score <- score_model(bts, genmatch.fs1.matched, df_rel_val)
genmatch.fs1.score
```

Number of Beta samples: `r nrow(genmatch.fs1.matched)`

```{r genmatch_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.matched, df_beta_val)
```

@@

```{r genmatch_fs1_500, echo=FALSE}
genmatch.fs1.500.matched <- df_train_gen[fs1_500_results$matches$index.control,]
genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.matched, df_rel_val)
genmatch.fs1.500.score
```

Number of Beta samples: `r nrow(genmatch.fs1.500.matched)`

```{r genmatch_fs1_500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
```

@@

```{r genmatch_fs3, echo=FALSE}
genmatch.fs3.matched <- df_train_gen[fs3_results$matches$index.control,]
genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.matched, df_beta_val)
genmatch.fs3.score <- score_model(bts, genmatch.fs3.matched, df_rel_val)
genmatch.fs3.score
```

Number of Beta samples: `r nrow(genmatch.fs3.matched)`

```{r genmatch_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs3.matched, df_beta_val)
```

@@

```{r genmatch_fs5, echo=FALSE}
genmatch.fs5.matched <- df_train_gen[fs5_results$matches$index.control,]
genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.matched, df_beta_val)
genmatch.fs5.score <- score_model(bts, genmatch.fs5.matched, df_rel_val)
genmatch.fs5.score
```

Number of Beta samples: `r nrow(genmatch.fs3.matched)`

```{r genmatch_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs5.matched, df_beta_val)
```

@@

Genetic matching produces the optimal matching results. It yields the lowest scores, without dropping large sample of the Beta profiles. Unsurprisingly, matching directly, and only, on the performance metrics yields the best results. Increasing the population size hyperparameter slightly decreased model performance, which is surprising. Considering this substantially increases training times, the lower value will be used.

@@

* matching algorithm: Genetic Matching
* features: Only performance metrics
* hyperparameters: Default for `Matching` library

@@

```{r serialize_gcp, echo=FALSE}
results_file_name = 'validation_results_20191106.RData'
results_file_path = file.path('data', results_file_name)

>>>>

extract_predictions <- function(matched, validation){
  prediction <- validation %>%
    filter(client_id %in% matched$client_id)

  return(prediction)
}
```

@@

```{r nn_mal_fs1, echo=FALSE}
# nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
#                         caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
nn.mal.fs1.predictions <- extract_predictions(nn.mal.fs1$matched, df_beta_val)
nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1.predictions, df_beta_val)
nn.mal.fs1.score <- score_model(bts, nn.mal.fs1.predictions, df_rel_val)
# nn.mal.fs1.score
```

Resultant scores: `r nn.mal.fs1.score`

* Number of matched Beta training samples: `r nrow(nn.mal.fs1$matched)`
* Number of matched Beta validation samples: `r nrow(nn.mal.fs1.predictions)`

```{r nn_mal_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs1.predictions, df_beta_val, nn.mal.fs1.qq)
```

@@

```{r nn_mal_fs3, echo=FALSE}
# nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
#                         caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
nn.mal.fs3.predictions <- extract_predictions(nn.mal.fs3$matched, df_beta_val)
nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3.predictions, df_beta_val)
nn.mal.fs3.score <- score_model(bts, nn.mal.fs3.predictions, df_rel_val)
# nn.mal.fs3.score
```

Resultant scores: `r nn.mal.fs3.score`

* Number of matched Beta training samples: `r nrow(nn.mal.fs3$matched)`
* Number of matched Beta validation samples: `r nrow(nn.mal.fs3.predictions)`

```{r nn_mal_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs3.predictions, df_beta_val)
```

@@

```{r nn_mal_fs5, echo=FALSE}
# nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
#                         caliper = 0, calclosest = TRUE, ratio = 1, 
#                         distance = "mahalanobis")
nn.mal.fs5.predictions <- extract_predictions(nn.mal.fs5$matched, df_beta_val)
nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5.predictions, df_beta_val)
nn.mal.fs5.score <- score_model(bts, nn.mal.fs5.predictions, df_rel_val)
# nn.mal.fs5.score
```

Resultant scores: `r nn.mal.fs5.score`

* Number of matched Beta training samples: `r nrow(nn.mal.fs5$matched)`
* Number of matched Beta validation samples: `r nrow(nn.mal.fs5.predictions)`

```{r nn_mal_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.mal.fs5.predictions, df_beta_val)
```

@@

```{r nn_logit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
# nn.linear.logit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
#                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
nn.linear.logit.fs1.predictions <- extract_predictions(nn.linear.logit.fs1$matched, df_beta_val)
nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1.predictions, df_beta_val)
nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1.predictions, df_rel_val)
# nn.linear.logit.fs1.score
```

Resultant scores: `r nn.linear.logit.fs1.score`

* Number of matched Beta training samples: `r nrow(nn.linear.logit.fs1$matched)`
* Number of matched Beta validation samples: `r nrow(nn.linear.logit.fs1.predictions)`

```{r nn_logit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs1.predictions, df_beta_val)
```

@@

```{r nn_logit_fs3, warning=FALSE, error=FALSE, echo=FALSE}
# nn.linear.logit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
#                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
nn.linear.logit.fs5.predictions <- extract_predictions(nn.linear.logit.fs5$matched, df_beta_val)
nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5.predictions, df_beta_val)
nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5.predictions, df_rel_val)
# nn.linear.logit.fs5.score
```

Resultant scores: `r nn.linear.logit.fs5.score`

* Number of matched Beta training samples: `r nrow(nn.linear.logit.fs5$matched)`
* Number of matched Beta validation samples: `r nrow(nn.linear.logit.fs5.predictions)`

```{r nn_logit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.logit.fs5.predictions, df_beta_val)
```

@@

```{r nn_gam_fs1, warning=FALSE, error=FALSE, echo=FALSE, message=FALSE}
# nn.gam.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
#                         caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
nn.gam.fs1.predictions <- extract_predictions(nn.gam.fs1$matched, df_beta_val)
nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1.predictions, df_beta_val)
nn.gam.fs1.score <- score_model(bts, nn.gam.fs1.predictions, df_rel_val)
# nn.gam.fs1.score
```

Resultant scores: `r nn.gam.fs1.score`

* Number of matched Beta training samples: `r nrow(nn.gam.fs1$matched)`
* Number of matched Beta validation samples: `r nrow(nn.gam.fs1.predictions)`

```{r nn_gam_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs1.predictions, df_beta_val)
```

@@

```{r nn_gam_fs5, warning=FALSE, error=FALSE, echo=FALSE}
# nn.gam.fs5 <- train_matchit(dfs[['4']], fs5, add_interactions = FALSE, replace = FALSE, 
#                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
nn.gam.fs5.predictions <- extract_predictions(nn.gam.fs5$matched, df_beta_val)
nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5.predictions, df_beta_val)
nn.gam.fs5.score <- score_model(bts, nn.gam.fs5.predictions, df_rel_val)
# nn.gam.fs5.score
```

Resultant scores: `r nn.gam.fs5.score`

* Number of matched Beta training samples: `r nrow(nn.gam.fs5$matched)`
* Number of matched Beta validation samples: `r nrow(nn.gam.fs5.predictions)`

```{r nn_gam_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.gam.fs5.predictions, df_beta_val)
```

@@

```{r nn_probit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
# nn.linear.probit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
#                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
nn.linear.probit.fs1.predictions <- extract_predictions(nn.linear.probit.fs1$matched, df_beta_val)
nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1.predictions, df_beta_val)
nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1.predictions, df_rel_val)
# nn.linear.probit.fs1.score
```

Resultant scores: `r nn.linear.probit.fs1.score`

* Number of matched Beta training samples: `r nrow(nn.linear.probit.fs1$matched)`
* Number of matched Beta validation samples: `r nrow(nn.linear.probit.fs1.predictions)`

```{r nn_probit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs1.predictions, df_beta_val)
```

@@

```{r nn_probit_fs5, warning=FALSE, error=FALSE, echo=FALSE}
# nn.linear.probit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
#                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
nn.linear.probit.fs5.predictions <- extract_predictions(nn.linear.probit.fs5$matched, df_beta_val)
nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5.predictions, df_beta_val)
nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5.predictions, df_rel_val)
# nn.linear.probit.fs5.score
```

Resultant scores: `r nn.linear.probit.fs5.score`

* Number of matched Beta training samples: `r nrow(nn.linear.probit.fs5$matched)`
* Number of matched Beta validation samples: `r nrow(nn.linear.probit.fs5.predictions)`

```{r nn_probit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, nn.linear.probit.fs5.predictions, df_beta_val)
```

@@

```{r genmatch_fs1, echo=FALSE}
genmatch.fs1.matched <- df_train_gen[fs1_results$matches$index.control,]
genmatch.fs1.predictions <- extract_predictions(genmatch.fs1.matched, df_beta_val)
genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.predictions, df_beta_val)
genmatch.fs1.score <- score_model(bts, genmatch.fs1.predictions, df_rel_val)
# genmatch.fs1.score
```

Resultant scores: `r genmatch.fs1.score`

* Number of matched Beta training samples: `r length(unique(genmatch.fs1.matched$client_id))`
* Number of matched Beta validation samples: `r nrow(genmatch.fs1.predictions)`

```{r genmatch_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.predictions, df_beta_val)
```

@@

```{r genmatch_fs1_500, echo=FALSE}
genmatch.fs1.500.matched <- df_train_gen[fs1_500_results$matches$index.control,]
genmatch.fs1.500.predictions <- extract_predictions(genmatch.fs1.500.matched, df_beta_val)
genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.predictions, df_beta_val)
genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.predictions, df_rel_val)
# genmatch.fs1.500.score
```

Resultant scores: `r genmatch.fs1.500.score`

* Number of matched Beta training samples: `r length(unique(genmatch.fs1.500.matched$client_id))`
* Number of matched Beta validation samples: `r nrow(genmatch.fs1.500.predictions)`

```{r genmatch_fs1.500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs1.500.predictions, df_beta_val)
```

@@

```{r genmatch_fs3, echo=FALSE}
genmatch.fs3.matched <- df_train_gen[fs3_results$matches$index.control,]
genmatch.fs3.predictions <- extract_predictions(genmatch.fs3.matched, df_beta_val)
genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.predictions, df_beta_val)
genmatch.fs3.score <- score_model(bts, genmatch.fs3.predictions, df_rel_val)
# genmatch.fs3.score
```

Resultant scores: `r genmatch.fs3.score`

* Number of matched Beta training samples: `r length(unique(genmatch.fs3.matched$client_id))`
* Number of matched Beta validation samples: `r nrow(genmatch.fs3.predictions)`

```{r genmatch_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs3.predictions, df_beta_val)
```

@@

```{r genmatch_fs5, echo=FALSE}
genmatch.fs5.matched <- df_train_gen[fs5_results$matches$index.control,]
genmatch.fs5.predictions <- extract_predictions(genmatch.fs5.matched, df_beta_val)
genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.predictions, df_beta_val)
genmatch.fs5.score <- score_model(bts, genmatch.fs5.predictions, df_rel_val)
#genmatch.fs5.score
```

Resultant scores: `r genmatch.fs5.score`

* Number of matched Beta training samples: `r length(unique(genmatch.fs5.matched$client_id))`
* Number of matched Beta validation samples: `r nrow(genmatch.fs5.predictions)`

```{r genmatch_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
plot_validation_results(df_rel_val, genmatch.fs5.predictions, df_beta_val)
```

@@

Nearest-Neighbors Probit, Linear produces the optimal matching results. It yields the lowest scores, without dropping large sample of the Beta profiles. Unsurprisingly, matching directly, and only, on the performance metrics yields the best results. Interestingly, it appears that interactions across covariates greatly help. Fortunately, this model architecture is relatively cheap from a computational perspective.

Balancing on additional covariates (e.g, FS3 or FS5), outside of the performance metrics, yields sub-optimal results. Nearest-Neighbors Probit, Linear again yields the lowest score (`r nn.linear.probit.fs5.score`); however, this is at the expense of a greatly reduced Beta samples size (`r nrow(nn.linear.probit.fs5.predictions)`). Genetic matching is able to retain a much larger sample size (`r nrow(genmatch.fs3.predictions)`), at the expense of greater error (`r genmatch.fs3.score`).

@@

* matching algorithm: Nearest-Neighbors Probit, Linear
* features: Only performance metrics
* hyperparameters: 
    * `caliper` = 0.4
    * `calcloset` = FALSE
    * `ratio` = 3
    * `replace` = FALSE
    * 4x oversampling
    * Interactions across covariates

@@

```{r serialize_gcp, echo=FALSE}
results_file_name = 'validation_results_20191121.RData'
results_file_path = file.path('data', results_file_name)
